Topic Scores

### 2019-02-20 test_delete_later_sofia.Rmd
clean

###Selecting key words
```{r}
test <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(3, beta) %>%
  group_by(topic) %>%
  summarise(key_words= list(Reduce(f= c, x = term)))

kw <- unique(Reduce(x = test$key_words, f= c))

kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl")

setdiff(kw, kw_stopwords)

>>>>

###Selecting key words
```{r}
top_kw <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(3, beta) %>%
  pull(term)

kw <- unique(top_kw)

kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl",
    #unsure:
               "theory", "search", "perspective"
                )
kw <- setdiff(kw, kw_stopwords)
